The `geomnet` package

### 2016-12-06 README.Rmd
add "singletons" parameter

```{r HPplot, fig.width=10, fig.align='center'}
library(geomnet)
head(hp.edges)
head(hp.chars)
hp.all <- fortify(as.edgedf(hp.edges), hp.chars, group = "book")
ggplot(data=hp.all, aes(from_id = from, to_id = to_id)) + 
  geom_net(fiteach=T, directed = T, size = 2, linewidth = .5, 
           ealpha = .5, labelon = T, fontsize = 2, repel = T, 
           labelcolour = "black", arrowsize = .5,
           aes(colour = house, group = house, shape = gender)) + 
  scale_colour_manual(values = c("#941B08","#F1F31C", 
                                 "#071A80", "#154C07")) + 
  facet_wrap(~book, labeller = "label_both") + 
  theme_net() + theme(panel.background = element_rect(colour = 'black'))
```

>>>>

```{r HPplot, fig.width=10, fig.height=8, fig.align='center', warning = FALSE}
library(geomnet)
head(hp.edges)
head(hp.chars)
hp.all <- fortify(as.edgedf(hp.edges), hp.chars, group = "book")
# only plot the characters with any connections in a given book. 
ggplot(data=hp.all, aes(from_id = from, to_id = to_id)) + 
  geom_net(fiteach=T, directed = T, size = 3, linewidth = .5, 
           ealpha = .5, labelon = T, fontsize = 3, repel = T, 
           labelcolour = "black", arrowsize = .5, singletons = FALSE,
           aes(colour = house, group = house, shape = gender)) + 
  scale_colour_manual(values = c("#941B08","#F1F31C", 
                                 "#071A80", "#154C07")) + 
  facet_wrap(~book, labeller = "label_both") + 
  theme_net() + theme(panel.background = element_rect(colour = 'black'))
```
